\documentclass[a4paper,10pt]{article}
\usepackage{paper-en}
\usepackage{hyperref}

\def\thetitle{Shadow isoperimetry}
\def\theauthors{}

\hypersetup{colorlinks=true,
citecolor=black,
linkcolor=black,
anchorcolor=black,
filecolor=black,
menucolor=black,
urlcolor=black,
pdftitle={\thetitle},
pdfauthor={\theauthors}
}
\begin{document}

\title{\thetitle}
\author{\theauthors}
\date{}
\maketitle

\begin{abstract}
We outline a proof of the isoperimetric inequality for Favard area.
\end{abstract}

\section{Introduction}


Given a compact subset $K\subset \RR^n$ let us denote by $a(K)$ its \emph{Favard area}; that is, the average of the areas of orthogonal projections of $K$ to hyperplanes.
Area and volume will mean the Lebesgue measures of dimension $n-1$ and $n$.

Since the dependence of the projection on the hyperplane in this case has closed graph, Fubini's theorem implies the integrability of the area of the projection as a function of the hyperplane, so the Favard area is well-defined.

\begin{thm}{Theorem}\label{thm:main}
Let $K\subset \RR^n$ be a compact subset and let $B\subset \RR^n$ be a ball.
Then
\[
a(K)= a(B)\quad\Rightarrow\quad \vol K\le \vol B.
\]
Moreover, if equality holds, then $K$ contains a congruent copy $B$ and the remaining part has vanishing volume.%
\footnote{Со случаем равенства надо разобраться, иначе странно.}
\end{thm}

By \cite[3.3.13]{federer}, this theorem gives a more exact version of the standard isoperimetric inequality.


In the proof we adapt the idea of Frederick Almgren, \cite[pp. 454--455]{almgren-1986}.

\section{Proofs}

Given a compact set $K$, consider the ball $B$ such that $a(K)=a(B)$. Let us denote by $\kappa=\kappa(K)$ the normal curvature of $\partial B$, so $\tfrac1\kappa$ is the radius of $B$ and
\[
\frac{\omega_{n-1}}{\kappa^{n-1}}=a(K)=a(B),\quad \frac{\omega_{n}}{\kappa^{n}}=\vol B,
\]
where $\omega_n$ is the volume of the unit ball in $\RR^n$.

\begin{thm}{Lemma}\label{lem:support}
Let $K$ be a compact set in $\RR^n$.
Given $\eps>0$, there is a strictly convex body $C$ with smooth boundary such that $C\supset K$,
$\partial C\cap K$ contains a single point, say $p$,
and the Gauss and mean curvatures of $\partial C$ at $p$ are at least $(\kappa(K)-\eps)^{n-1}$ and $(n-1)\cdot (\kappa(K)-\eps)$, respectively.
\end{thm}

\begin{proof}
Let us denote by $K_s$ the closed $s$-neighborhood of $K$. Good thing about $K_s$ is that the convex hull $\conv K_s$ has $C^1$-smooth boundary and its second derivatives exist almost everywhere and are bounded.
So the shape operator ($\Shape$), the Gauss curvature $G=\det(\Shape)$, and mean curvature $H=\tr(\Shape)$ are defined almost everywhere on $\partial(\conv K_s)$. Note also that any hyperplane projection of $K_s$ is the closed $s$-neighborhood of the projection of $K$ to the same hyperplane, which implies continuous dependence of the area of the projection on $s\ge 0$.

Define the \emph{contact boundary} of $K_s$ as
\[
\cont K_s=K_s\cap\partial(\conv K_s).
\]
Since every linear function attains its maximum on $\conv K_s$ in a point of $K_s$, the normals of $\cont K_s$ constitute the whole sphere.
Hence,
\[
\int\limits_{x\in \cont K_s}G(x)=\area \SSS^{n-1}=n\cdot\omega_n.
\]
Therefore, for any $\delta>0$ the inequality
\[
G(x)\ge \frac{\area \SSS^{n-1}}{\area (\cont K_s)}-\delta = \frac{n\omega_n}{\area (\cont K_s)}-\delta
\]
holds for $x$ in a set of positive measure of $\cont K_s$.

From the inclusion $\cont K_s\subseteq K_s$ it follows that
\[
a(\cont K_s)\le a(K_s).
\]
Further, since $\cont K_s\subset \partial (\conv K_s)$, the Crofton formula implies
\[
\area (\cont K_s)\le \frac{n\cdot\omega_n}{\omega_{n-1}}\cdot a(\cont K_s);
\]
the constant $\tfrac{n\cdot\omega_n}{\omega_{n-1}}$ here is the optimal constant (so we have equality if $\cont K_s$ is a closed convex hypersurface).

Combining the last three inequalities and the definition of $\kappa(K_s)$ and its continuity in $s$ we get a point $x\in \cont K_s$ with well-defined shape operator and Gauss curvature at least $(\kappa(K_s)-\eps)^{n-1}$.

Let us take a smooth hypersurface $W_s$ with slightly smaller (with positive definite difference) shape operator at $x$ compared to that of $\partial(\conv K_s)$ that touches $K_s$ as a single point $x$.
Note that all the curvatures of $\partial \conv K_s$ were at most $1/s$, so all the curvatures of $W_s$ may be assumed strictly smaller than $1/s$.


Let $W$ be the $s$-equidistant hypersurface of $W_s$.
Note that $W$ touches $K$ in a single point, say $p$, which is the nearest-point projection of $x$ to $K$.
From the above observation on curvatures it follows that $W$ is still convex and smooth at $p$.
It remains to take a small smooth closed strictly convex neighborhood $N$ of $\conv K$, chop it by $W$ and smooth the resulting body near the corner $W\cap \partial N$ while keeping it strictly convex.
The hypersurface $W$ was already strictly convex, so $C$ is strictly convex in a neighborhood of $p$.
It may be made strictly convex by smoothing its support function outside of the corresponding neighborhood of the normal at $p$.

The bound on the mean curvature follows from the inequality of arithmetic and geometric means.
\end{proof}


\begin{thm}{Lemma}\label{lem:variation}
Let $C$, $K$, and $p$ be as in the previous lemma, and let
\[
K_t=\set{x\in K}{\dist(\partial C, x)\ge t}.
\]
Then
\[
(1+o_t(1))\cdot(\vol K-\vol K_t)\le \frac{n\cdot \omega_n}{\omega_{n-1}\cdot H(p)}\cdot(a(K)-a(K_t)),
\]
where $H(p)$ denotes the mean curvature of $\partial C$ at $p$.
\end{thm}

\begin{proof}
Let $u\in \SSS^{n-1}$ and $r\in \RR$.
Consider the unique point $\bar x(u)\in \partial C$ with outer normal vector $u$.
Then the map
\[
\xi\:(u,r)\mapsto\bar x(u)-r\cdot u
\]
gives a smooth parametrization of a neighborhood of $\partial C$.
Denote by $u_0$ the unit normal vector at $p$, so $p=\xi(u_0,0)$.

Denote by $\mathbf 1_K$ the characteristic function of $K$ and let $\phi(u,r)=\mathbf 1_K\circ \xi(u,r)$.
Then
\begin{align*}
\vol K-\vol K_t
=
&\int\limits_{u\in \SSS^{n-1}}
\int\limits_{r\in [0,t]} \phi(u,r)\cdot J(u,r)=
\\
=
\frac{n\cdot \omega_n\cdot (1+o_t(1))}{G(p)}
\cdot
&\oint\limits_{u\in \SSS^{n-1}}
\int\limits_{r\in [0,t]} \phi(u,r),
\end{align*}
where $\oint$ denotes the average along the sphere and $J(u,r)$ is the Jacobian of $\xi$ at $(u,r)$.
The last equality follows since $J(u_0,0)=1/G(p)$ and if $r\le t$ for small $t>0$, then $\phi(u,r)\ne 0$ only if $u$ is in a sufficiently small neighborhood of $u_0$, so we may approximate the Jacobian by its value at $(u_0,0)=\xi^{-1}(p)$.

Let us turn to hyperplane projections.
Choose a unit vector $w$; denote by $L$ and $L_t$ the projections of $K$ and $K_t$ to $w^\perp$.
The $t$-neighborhood of $L_t$ is contained in the projection of $C$, so $L_t$ is at distance at least $t$ from the boundary of the projection of $C$.
This allows us to estimate
\[
\area L-\area L_t
\ge
\int\limits_{u\in \SSS^{n-2}}
\int\limits_{r\in [0,t]}
\phi(u,r)\cdot J_w(u,r).
\]
where $\SSS^{n-2}=\SSS^{n-1}\cap w^\perp$ and
$J_w(u,r)$ denotes the Jacobian at $(u,r)$ of the projection  to $w^\perp$ of the restriction $\xi|_{\SSS^{n-2}\times \RR}$. This estimate holds true since the points with $\phi(u,r)=1$ are projected injectively to $L$ with the Jacobian $J_w$ and do not get into $L_t$.

If $t$ is sufficiently small, then $\phi(u,r)\ne 0$ only if $u$ lies in a sufficiently small neighborhood of $u_0$.
This implies that $w$ may be considered almost perpendicular to $u_0$, which we assume further.

Denote by $w'$ the vector closest to $w$ in $\SSS^{n-1}\cap u_0^\perp$.
If $\phi(u,r)\ne 0$ and $0\le r\le t$, then from the uniform continuity of $J_w$
\[
J_w(u,r)=(1+o_t(1))\cdot J_{w'}(u_0,0)=(1+o_t(1))\cdot \frac{k(w')}{G(p)},
\]
where $k(w')$ denotes normal curvature of $\partial C$ in the direction $w'$ at $p$. The last equality can be understood by approximating $C$ with a graph of a quadratic function, noting that a projection corresponds to the restriction of its dual, and noting that a diagonal element of an inverse matrix (corresponding to $k(w')$) is an $(n-2)\times (n-2)$ minor of the original matrix (corresponding to the Gaussian curvature of the projection) divided by the determinant of the whole matrix (corresponding to the Gaussian curvature before the projection).

Note that $\tfrac{1}{n-1}\cdot H(p)$ is the average of $k(w')$ for $w'\perp u_0$.
Therefore, taking the average, we get
\[
a(K)-a(K_t)\ge \frac {H(p)\cdot \omega_{n-1}\cdot(1+o_t(1))}{ G(p)} 
\cdot\oint\limits_{u\in \SSS^{n-1}}
\int\limits_{r\in [0,t]}
\phi(u,r).
\]
We used that averaging over the whole sphere is the same as averaging over a variable point in a subsphere and then averaging over subspheres.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:main}.]
Assume that $K$ is a counterexample.
Then, we can choose $\delta>0$ such that
\[
s_\delta(K) \df \vol K - (1+\delta)\cdot \vol B > 0,
\]
where $B$ denotes the ball such that $a(K)=a(B)$.

Remove from $K$ the set of measure zero of its points of zero density and then pass to the closure.
After this procedure, $K$ remains compact, its volume did not change while Favard area $a(K)$ may decrease.
Moreover, now nonempty intersections of $K$ with open sets have positive volume.
This ensures that the volume cut from $K$ by the procedure of Lemma~\ref{lem:variation} will be positive.

Applying Lemma~\ref{lem:variation} to $C$ and $p$ provided by Lemma~\ref{lem:support}, we get a compact set $K'\subset K$ such that
\[s_\delta(K')>s_\delta(K).\]

%\[\vol K-\vol K'< \left( \frac{n\omega_n}{(n-1)\omega_{n-1}\kappa(K)}+\eps\right)\cdot (a(K)-a(K')).\]
%Noting that $\kappa(K)=\tfrac{\omega_{n-1}^{1/(n-1)}}{a(K)^{1/(n-1)}}$, we transform this into
%\[\vol K-\vol K'< \left( \frac{n\omega_n a(K)^{1/(n-1)}}{(n-1)\omega_{n-1}^{n/(n-1)}}+\eps\right)\cdot (a(K)-a(K')).\]
%and applying the definition of $c_n$:
%\[\vol K-\vol K'< \left( c_n\frac{n}{(n-1)}a(K)^{1/(n-1)}+\eps \right)\cdot (a(K)-a(K')).\]
%Considering the derivatives of $s_\delta(K)$ as a function of $\vol$ and $a$ one observes that
%\[\frac{\partial s_\delta(K)}{\partial\vol} = 1,\quad \frac{\partial s_\delta(K)}{\partial a(K)} = (1+\delta)c_n\frac{n}{n-1} a(K)^{1/(n-1)}\]
%and therefore, for an appropriate choice of $\eps>0$, we get $s_\delta(K')>s_\delta(K)$ for the chopped body $K'$.

Now consider an inclusion chain $\mathcal Z$ of compact subsets $L\subset K$ satisfying $s_\delta(L)\ge s_0$ for all $L\in\mathcal Z$, where $s_0=s_\delta(K) > 0$.
The intersection of the chain is a compact set $M$.
By the outer regularity of the Lebesgue measure there exists an open $U\supseteq M$ whose volume is arbitrarily close to $\vol M$.
Since every $L\in\mathcal Z$ is compact and $M$ does not intersect the complement of $U$, some $L\in\mathcal Z$ lies in $U$.
Hence $\vol L\le\vol U$ and can be made arbitrarily close to $\vol M$.
It is also clear that $a(L)\ge a(M)$ for any $L\in\mathcal Z$.
Hence $s_\delta(M)$ must be at least $s_0$.

Applying Zorn's lemma to the compact subsets of $K$ satisfying $s_\delta(L)\ge s_0$, we get an inclusion-minimal such set $M$.
But the above argument applied to $M$ in place of $K$ contradicts the minimality.
\end{proof}

{\sloppy
\def\emph{\textit}
\printbibliography[heading=bibintoc]
\fussy
}

\end{document}
